Aligning species range data to better serve science and conservation

### 2015-12-24 data_explore/data_explore.Rmd
updating manuscript

source('data_explore_fxns.R')
### When knitting this, it automatically sets WD to be this directory...
```

@@

scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  labs(x = bquote('Area alignment '*alpha['area']*' (%)'), 
       y = bquote('Distribution alignment '*alpha['dist']*' (%)'), 
       title = 'Distribution alignment vs area alignment',
       color = 'Risk', size = '% ocean range')

@@

@@

@@

spp_list1 <- spp_list %>%
  group_by(popn_category) %>%
  mutate(n_spp = n()) %>%
  ungroup()

>>>>

setwd('data_explore')
source('data_explore_fxns.R')
### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk
```

@@

scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  labs(x = bquote('Extent alignment '*alpha['ext']*' (%)'), 
       y = bquote('Distribution alignment '*alpha['dist']*' (%)'), 
       title = 'Distribution alignment vs Extent alignment',
       color = 'Risk', size = '% ocean range')

@@

spp_list_quads <- spp_list1 %>%
  mutate(quad = NA,
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q1$sciname, 'q1', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q2$sciname, 'q2', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q3$sciname, 'q3', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q4$sciname, 'q4', quad))
write.csv(spp_list_quads, file.path(dir_data, 'spp_list_quads.csv'), row.names = FALSE)

@@

write.csv(spp_gp_quadrants, file.path(dir_data, 'spp_gp_quads.csv'), row.names = FALSE)

@@

### 2015-12-24 ms_0_main.Rmd
updating manuscript

---
title: "Aligning species range data to better serve science and conservation"
author: "Casey O'Hara, Jamie Afflerbach, Ben Halpern"
output:
  pdf_document:
    number_sections: yes
    toc: no
  html_document:
    highlight: haddock
    number_sections: yes
    theme: spacelab
    toc: yes
  word_document: default
---

@@

``` {r abstract, child = 'ms_2_intro_res_disc.Rmd'}
```

@@

``` {r abstract, child = 'ms_3_methods.Rmd'}
```

@@

``` {r abstract, child = 'ms_4_figs.Rmd'}
```

@@

``` {r abstract, child = 'ms_5_refs.Rmd'}
```

>>>>

---
title: "Aligning species range data to better serve science and conservation"
author: "Casey O'Hara, Jamie Afflerbach, Ben Halpern"
output:
  html_document:
    highlight: haddock
    number_sections: yes
    theme: spacelab
    toc: no
  pdf_document:
    number_sections: yes
    toc: no
  word_document: default
---

@@

``` {r intro_results_discussion, child = 'ms_2_intro_res_disc.Rmd'}
```

@@

``` {r methods, child = 'ms_3_methods.Rmd'}
```

@@

``` {r figures, child = 'ms_4_figs.Rmd'}
```

@@

``` {r references, child = 'ms_5_refs.Rmd'}
```

### 2015-12-24 ms_2_intro_res_disc.Rmd
updating manuscript

Importantly, biases in taxonomic or spatial coverage of a dataset could shift management or conservation actions _towards places or species that aren’t actually the most in need (shift management or conservation actions away from places or species that are most in need?)_.(maybe Jetz 2008?) False indications of presence (commission errors) overestimate the protection afforded by a marine reserve, while false indications of absence (omission errors) reduce the adequacy of a reserve system by underestimating species distributions. (Rondinini et al. 2006)

To understand the implications of similarities and differences between the two datasets, we examined how they compare in their representation of global spatial distribution of species, and for the relatively small number of species represented in both datasets, how closely their spatial distribution maps align. _We then reanalyze two recent studies using these datasets based on different versions of the data to illustrate how and why decisions about which species range data to use affect our understanding of the status of marine biodiversity._

@@

The IUCN publishes species distribution maps as vector shapefiles gathered into taxonomic groups _that have been comprehensively assessed (> 90% of species evaluated)_.  Species extents of occurrence are outlined by experts based upon known occurrences of the species, typically from point locality databases such as the Ocean Biogeographic Information System (OBIS) (REF) and the Global Biodiversity Information Facility (GBIF) (REF), and refined by expert understanding of range and habitat preferences.

_IUCN publishes range map sets only for taxonomic groups that have been "comprehensively assessed," i.e. in which at least 90% of the species within the taxonomic group have been evaluated_.  While this mitigates sampling bias within taxa, it also means that entire taxonomic groups remain unavailable until they have met this threshold of comprehensive assessment.

AquaMaps develops species distribution maps based on modeled relative environmental suitability.  For each modeled species, environmental preferences (e.g. temperature, depth, salinity) are deduced from occurrence records such as OBIS and GBIF, published species databases such as FishBase, and expert knowledge.  These environmental preferences are compared to a map of environmental attributes on a 0.5 degree global grid, creating a global map of probability of occurrence.

@@

Differences in methodology and intent drive significant differences between AquaMaps and IUCN species distribution maps (Fig. 1).  Only `r n_spp_both` species were included in both datasets (`r p_both_am`% of total Aquamaps species; `r p_both_iucn`% of total IUCN species; Fig. 1, 2).  __All IUCN-mapped species are also included in Red List species, but only `r p_spp_am_rl`% of AquaMaps species.__

@@

The balance of species represented in IUCN spatial data skews toward tropical latitudes compared to the distribution represented in AquaMaps distribution maps.  This may be driven by the fact that the taxonomic distribution of IUCN distribution maps focuses heavily on coral reef-associated species (see fig. XXX).  While both datasets indicate highest species richness in the Coral Triangle and western Indian Ocean, the AquaMaps dataset shows a relatively larger representation of species in the Atlantic, Caribbean, and eastern Pacific than does the IUCN dataset.

Each dataset offers spatial distribution information for large numbers of species.  However, the datasets vary in terms of taxonomic coverage and regional coverage.  For spatial assessments of biodiversity, the choice of one dataset over the other is likely to create significantly different results.  For studies confined to a narrow range of taxa or to a narrow spatial scale, one dataset may offer an advantage over the other in the number of species maps available.  For global scale biodiversity studies, however, the selection of one dataset over the other will entail tradeoffs in spatial coverage, taxonomic breadth, and taxonomic depth. ___find a reference that describes what makes a "good" dataset for global biodiversity, e.g. OHI___ _or maybe species richness vs diversity vs "health" or whatnot_

@@

For species described in both spatial datasets, we would expect to see spatial correlation both in the global pattern of species distribution and the extent of species range.  Large discrepancies in distribution and range extent could indicate species that require further study to consolidate expert knowledge for IUCN range maps and improve the accuracy of AquaMaps species distribution models.

Using genus and species binomials to identify paired maps, we selected the subset of marine species that have range maps in both IUCN and AquaMaps current native distribution (n = `r nrow(spp_map_pairs)`).  We found that for `r round(nrow(spp_map_pairs %>% filter(sm_range == 'AM')) / nrow(spp_map_pairs) * 100, 1)`% of paired-map species, the IUCN distribution maps indicated a larger species range than the range indicated by AquaMaps.  This aligns with the expectations of Rondinini et al. (2006) that range maps are more likely to falsely predict presence while predicted distribution models are more likely to falsely predict absence.

Overlaying paired distribution maps for a given species, we calculated two dimensions of spatial alignment: _distribution alignment_, which we defined as the proportion of the smaller range intersecting the larger range; and _extent alignment_, which we defined as the ratio of the smaller range to the larger range.

For a species whose distribution is well understood and described in both datasets, we would expect to see a value near 100% for each dimension of alignment, indicating near-total inclusion of the smaller range within the larger (_distribution alignment_) and similar extent of occurrence (_extent alignment_).  Dividing the map-paired species into quadrants based on median values for each axis, we can examine the implications of four different qualities of alignment.

<!--
___moving to figure caption.  Summarize results here.___

* The upper right quadrant (quadrant 1) comprises species whose maps largely agree (better than median value) in both spatial distribution and the extent of described ranges.  For these species, the expert-drawn range map and the bioclimatic envelope model produce similar predictions of species distribution.  
* Species map pairs that fall within the upper left quadrant (quadrant 2: well-aligned in distribution but poorly-matched in extent) indicate species in which the range of the smaller map falls generally within the larger map, but the larger map may include more generous buffers or may include areas unrepresented in the smaller map.
* The lower right quadrant (quadrant 3: well-aligned in extent but poorly matched in distribution) includes species for which the paired maps generally agree in range extent, but disagree in locations of those ranges.  Disagreement in distribution seems to indicate a greater issue than disagreement in extent, so we categorized map pairs in this quadrant as being lower quality alignment than map pairs in either of the upper quadrants. 
* The lower left quadrant (quadrant 4: poorly matched in both dimensions) indicates species for which the map pairs fail to agree in both extent and distribution.

-->

Breaking down the quadrants by IUCN extinction risk categories, we found that species with higher extinction risk tend to be better aligned between the two datasets, perhaps correlated to increased expert scrutiny.  Does higher perceived risk lead to increased attention, and thus better understanding of species distribution? Or conversely, does increased attention to species distribution reveal deeper risk?  Likely both mechanisms are at play in a feedback loop.

Examining quadrants by taxonomic group, we found that certain taxa were far more likely than others to be spatially well-aligned; in particular, wide-ranging pelagic organisms such as marine mammals, tunas, and billfishes were more consistently well-aligned (quadrants 1 and 2) than demersal and reef organisms.   Coral species are predominantly found in quadrant 2, indicating that while general global distribution trends seem to be consistent between the two datasets, predicted extents are not well-aligned. AquaMaps accounts for seafloor depth as a limiting factor, highly constraining the predicted habitat for photosynthesizing corals, while IUCN maps for coral species often include wide buffers that would extend far beyond appropriate depth for coral habitat, thus likely overestimating the actual species range (see SI).  A similar mechanism may also drive poor extent alignment of other demersal and reef-associated organisms.

Poorly-aligned rangemaps, regardless of taxon or extinction risk category, indicate species that could benefit from further expert study.

___Other hypotheses/case studies to highlight other possible mechanistic differences?___

Confusion in species names also seems to correlate with spatial misalignment.  AquaMaps identifies each species map by binomial as well as a unique species ID code.  While the IUCN assigns a unique numeric code to every Red List-assessed species, this code is not used consistently to identify range map polygons. ___NOTE: NEW DATA as of Nov 24?  Need to re-extract all the IUCN species :( ___

___range maps less likely to commit omission errors and more likely to commit commission errors; predicted distribution moderate chance of each compared to range maps and point locality data___ (based on Rondinini et al. 2006) this in discussion after the distribution/extent analysis

@@

___do the analysis...___

Predictions:

IUCN overestimates extent esp for coastal species?  More species will be included in MPAs so fewer apparent gap species.  Included range area inside MPAs will increase.  Policy implications?  Less pressure to carefully consider MPA design; less resolution on

>>>>

Importantly, biases in taxonomic or spatial coverage of a dataset could shift management or conservation actions _towards places or species that aren’t actually the most in need (shift management or conservation actions away from places or species that are most in need?)_.(maybe Jetz 2008?) Errors of commission (false indications of presence) or omission (false indications of absence) could lead to inefficient or ineffective marine reserve systems and management plans. (Rondinini et al. 2006) (Jetz 2008?)

To understand the implications of differences between the two datasets, we compared how each data set represents the global spatial distribution of species.  For the relatively small number of species mapped in both datasets, we examined how well their spatial distribution maps align. We then subjected two recent marine biodiversity studies to a sensitivity analysis, highlighting the consequences of different data use decisions _on our understanding of the status of marine biodiversity._

@@

The IUCN publishes species distribution maps as vector shapefiles, collected by taxonomic groups.  Species experts outline polygons to represent a species' extent of occurrence, based on observation records <!--point locality databases such as the Ocean Biogeographic Information System (OBIS) (REF? not actually using this data) and the Global Biodiversity Information Facility (GBIF) (REF?),--> and refined by the expert's understanding of the species' range and habitat preferences.  IUCN publishes range map sets only for taxonomic groups that have been "comprehensively assessed," i.e. in which at least 90% of the species within the taxonomic group have been evaluated.  While this mitigates sampling bias within taxa, it also means that entire taxonomic groups remain unavailable until they have met this threshold of comprehensive assessment.

AquaMaps develops species distribution maps based on modeled relative environmental suitability.  For each modeled species, environmental preferences (e.g. temperature, depth, salinity) are deduced from occurrence records _such as OBIS and GBIF_ ___(should we mention these, or leave out? I left them out when describing the IUCN data sets)___, published species databases such as FishBase, and expert knowledge.  The AquaMaps model overlays these environmental preferences atop a map of environmental attributes on a 0.5 degree global grid, creating a global map of probability of occurrence.

@@

IUCN maps are best categorized as geographic range data, while AquaMaps maps can be categorized as predicted distribution data (Rondinini et al., 2006) _(the categories come from here, but not my categorizations of these particular datasets...)_; the two types of spatial data differ in methodology and intent, and this drives significant differences between the resulting species distribution maps (Fig. 1).  Only `r n_spp_both` species were included in both datasets (`r p_both_am`% of total Aquamaps species; `r p_both_iucn`% of total IUCN species; Fig. 1, 2).  _All IUCN-mapped species are also included in Red List species, but only `r p_spp_am_rl`% of AquaMaps species._

@@

The distribution of IUCN-mapped species skews toward tropical latitudes and away from the Atlantic and Eastern Pacific compared to the distribution of AquaMaps-mapped species.  This skew likely reflects the fact that the IUCN dataset focuses more heavily on coral reef-associated taxa than does the AquaMaps dataset (see fig. XXX).

Each dataset offers spatial distribution information for large numbers of species.  However, the datasets vary in terms of taxonomic coverage and regional coverage.  For spatial assessments of biodiversity, the choice of one dataset over the other is likely to create significantly different results.  For studies confined to a narrow range of taxa or to a narrow spatial scale, one dataset may offer an advantage over the other in the number of species maps available.  For global scale biodiversity studies, however, the selection of one dataset over the other will entail tradeoffs in spatial coverage, taxonomic breadth, and taxonomic depth._use something from Rondinini here?_

_find a reference that describes what makes a "good" dataset for global biodiversity, e.g. OHI, or maybe species richness vs diversity vs "health" or whatnot:  (Tittensor et al., 2010)_

@@

The IUCN and AquaMaps spatial datasets share `r nrow(spp_map_pairs)` species in common.  If we were to examine each species' pair of maps side by side, we would hope to see spatial correlation both in the global pattern of species distribution (where on the map) and the extent of species range (how much of the map).  Large discrepancies in distribution and range extent could indicate species that require further study to consolidate expert knowledge for IUCN range maps and improve the accuracy of AquaMaps species distribution models.

For each paired-map species, we calculated two dimensions of spatial alignment: _distribution alignment_, which we defined as the proportion of the smaller range intersecting the larger range (where on the map); and _extent alignment_, which we defined as the ratio of the smaller range to the larger range (how much of the map).  For a species whose distribution is well understood and described in both datasets, we would expect to see a value near 100% for each dimension of alignment.

We found that for `r round(nrow(spp_map_pairs %>% filter(sm_range == 'AM')) / nrow(spp_map_pairs) * 100, 1)`% of paired-map species, the IUCN distribution map indicated a larger species range than the AquaMaps map.  This concurs with the general expectation that geographic range maps (e.g. IUCN) are more likely to over-predict presence than predicted distribution models (e.g. AquaMaps), while predicted distribution models are more likely to over-predict absence.(Rondinini et al., 2006) _errors of commission vs errors of omission, essentially type I and type II errors_

Dividing the map-paired species into quadrants based on median values for each dimension, we can examine the _implications_ of four different qualities of alignment. (FIG 3a)

``` {r load_spp_list_by_quad, echo = FALSE}
spp_list_quads <- read.csv('data/spp_list_quads.csv', stringsAsFactors = FALSE)
n_q1 <- nrow(spp_list_quads %>% filter(quad == 'q1'))
n_q2 <- nrow(spp_list_quads %>% filter(quad == 'q2'))
n_q2_am_sm  <- nrow(spp_list_quads %>% filter(sm_range == 'AM' & quad == 'q2'))
n_q2_corals <- nrow(spp_list_quads %>% filter(str_detect(tolower(spp_group), 'coral') & quad == 'q2'))
n_corals    <- nrow(spp_list_quads %>% filter(str_detect(tolower(spp_group), 'coral')))
n_q3 <- nrow(spp_list_quads %>% filter(quad == 'q3'))
n_q4 <- nrow(spp_list_quads %>% filter(quad == 'q4'))
```

___could use some help on organizing this part... too much info?  should some go in the caption, and some in the body? thinking this way: quickie description of quadrants in caption of figure; then use the bar charts in Fig 4 to help explain some mechanisms of quadrants___

* The upper right quadrant (quadrant 1) comprises species whose maps largely agree (better than median value) in both spatial distribution and the extent of described ranges, as we hoped for well-understood species.  Excellent, but not particularly interesting.  
* Species map pairs that fall within the upper left quadrant (quadrant 2) agree well in distribution, but disagree in extent.
* The lower right quadrant (quadrant 3 ___note, "math" quadrant 3 would be lower left, not lower right, will this quadrant ID scheme be confusing?___) includes species for which the paired maps generally agree in range extent, but disagree on where those ranges lie - a more worrisome mismatch than that indicated by quadrant 2.
* The lower left quadrant (quadrant 4) indicates species for which the map pairs fail to agree in both extent and distribution.

Examining spatial alignment by taxonomic group (FIG 3a), we found that certain taxa were far more likely than others to be spatially well-aligned; in particular, wide-ranging pelagic organisms such as marine mammals, tunas, and billfishes were more consistently well-aligned (quadrants 1 and 2) than demersal and reef organisms.  _explain reasoning?_

Coral species are predominantly found in quadrant 2 (`r n_q2_corals` coral species - `r round(n_q2_corals/n_corals * 100, 1)`% of all corals and `r round(n_q2_corals/n_q2 * 100, 1)`% of all species in quadrant 2). <!--AquaMaps accounts for seafloor depth as a limiting factor, highly constraining the predicted habitat for photosynthesizing corals, while IUCN maps for coral species often include wide buffers that would extend far beyond appropriate depth for coral habitat, thus likely overestimating the actual species range (see SI).  A similar mechanism may also drive poor extent alignment of other demersal and reef-associated organisms.-->

___how to transition from above paragraph to this idea:___ Looking more closely at the species included in quadrant 2, we can identify several mechanisms that could cause extent misalignment.  For `r n_q2_am_sm` of `r n_q2` species in this quadrant (`r round((n_q2_am_sm/n_q2) * 100, 1)`%), the IUCN extent is larger than the AquaMaps extent.  By itself, this is not surprising; but for many of these species, a quick look at the maps (see SI for examples) shows that the IUCN range hews closely to the AquaMaps range, while including a wide buffer zone.  We suspect that many of these extent-misaligned map pairs can be easily explained: most corals and reef-associated organisms prefer shallower waters; seafloor depth is explicitly modeled in AquaMaps, but not explicitly included in IUCN range considerations.

* _Occasionally, the AquaMaps map conformed to a small, local subset of the IUCN map (see SI for examples), in some cases due to some point locality observations being rejected by AquaMaps experts (EXAMPLES) and in other cases due to differences in species identification._ ___bleh - this needs help.___

Breaking down the quadrants by IUCN extinction risk categories (FIG 3c), we found that species with higher extinction risk tend to be better aligned between the two datasets, perhaps correlated to increased expert scrutiny.  Does higher perceived risk lead to increased attention, and thus better understanding of species distribution? Or conversely, does increased attention to species distribution reveal more species at risk?  Likely both mechanisms are at play on a case-by-case basis, depending on the species' taxon and region. _does this argument bear up to closer scrutiny? CR isn't dominated by Q1 any more_

Poorly-aligned rangemaps, regardless of taxon or extinction risk category, indicate species that could benefit from further expert study. ___is this just 'duh'? is there something more important I can say?___

_Other hypotheses/case studies to highlight other possible mechanistic differences?_

@@

_do the analysis..._

_Predictions:  IUCN overestimates extent esp for coastal species?  More species will be included in MPAs so fewer apparent gap species.  Included range area inside MPAs will increase.  Policy implications?  Less pressure to carefully consider MPA design; less resolution on_

### 2015-12-24 ms_3_methods.Rmd
updating manuscript... adding a few annotated refs
updating manuscript

___Either move to brief methods section above, and maybe even shorten - BH___: To examine the overall taxonomic distribution across the spatial datasets, we grouped species by taxonomic class and data source (IUCN, AquaMaps, or both), and examined the proportion of each class represented in each data source category.  We further divided the data by whether species had been evaluated for the IUCN Red List of Threatened Species.

@@

For our comparisons of global distribution of represented biodiversity and spatial alignment between datasets, we considered "present" to be any cell with a non-zero probability of occurrence, to approximate the presence criteria used by IUCN.  To examine the effect of different presence threshold selections on the represented range of a species, we varied the threshold from 0.05 to 1.00 and calculated the average species range relative to a zero threshold.

@@

>>>>

___Either move to brief methods section above, and maybe even shorten - BH___: To examine the overall taxonomic distribution across the spatial datasets, we grouped species by taxonomic class and data source (IUCN, AquaMaps, or both), and examined the proportion of each class represented in each data source category.  We then filtered the species list to those that have been evaluated for the IUCN Red List of Threatened Species.

@@

For our comparisons of global distribution of represented biodiversity and spatial alignment between datasets, we considered "present" to be any cell with a non-zero probability of occurrence, to best approximate the "extent of occurrence" as generally indicated by IUCN maps.  To examine the effect of different presence threshold selections on the represented range of a species, we varied the threshold from 0.05 to 1.00 and calculated the average species range relative to a zero threshold.

@@

Using genus and species binomials to identify paired maps, we selected the subset of marine species that have range maps in both IUCN and AquaMaps current native distribution (n = `r nrow(spp_map_pairs)`).

### 2015-12-24 ms_4_figs.Rmd
updating manuscript

Figure 2 (a, b):

@@

Figure 3:

@@

___Figure XXX: Distribution alignment vs area alignment for `r nrow(spp_map_pairs)` species mapped in both Aquamaps and IUCN species distribution maps.___

Figure 4 (a, b):

@@

Figure 5 (a, b):

@@

Figure 6

>>>>

Number and proportion of species, listed by taxa, included in each dataset: IUCN, AquaMaps, or both. (a) All species with distribution maps; (b) IUCN Red List-assessed species with distribution maps.

### Figure 2 (a, b):

@@

Global marine species richness according to (a) AquaMaps dataset and (b) IUCN dataset.

### Figure 3 (a):

@@

Distribution alignment vs Extent alignment for `r nrow(spp_map_pairs)` species mapped in both Aquamaps and IUCN datasets.

``` {r tally_quad_counts, echo = FALSE}
dist_median <- round(median(spp_map_pairs$sm_perc,    na.rm = TRUE), 1)
area_median <- round(median(spp_map_pairs$area_ratio, na.rm = TRUE), 1)
q1_count <- sum(spp_map_pairs$sm_perc >= dist_median & spp_map_pairs$area_ratio >= area_median)
q2_count <- sum(spp_map_pairs$sm_perc <  dist_median & spp_map_pairs$area_ratio >= area_median)
q3_count <- sum(spp_map_pairs$sm_perc >= dist_median & spp_map_pairs$area_ratio <  area_median)
q4_count <- sum(spp_map_pairs$sm_perc <  dist_median & spp_map_pairs$area_ratio <  area_median)
```

* The upper right quadrant (quadrant 1) comprises species whose maps largely agree (better than median value) in both spatial distribution and the area of described ranges.
(n = `r q1_count`; `r round(q1_count/nrow(spp_map_pairs) * 100, 1)` %)
* The upper left quadrant (quadrant 2) comprises species whose maps agree well in distribution, but disagree in extent.
(n = `r q2_count`; `r round(q2_count/nrow(spp_map_pairs) * 100, 1)` %)
* The lower right quadrant (quadrant 3) includes species for which the paired maps generally agree in range extent, but disagree on where those ranges lie - a more problematic mismatch than that indicated by quadrant 2.
(n = `r q3_count`; `r round(q3_count/nrow(spp_map_pairs) * 100, 1)` %)
* The lower left quadrant (quadrant 4) indicates species for which the map pairs fail to agree in both area and distribution. 
(n = `r q4_count`; `r round(q4_count/nrow(spp_map_pairs) * 100, 1)` %)

### Figure 3 (b, c):

@@

Spatial alignment of paired-map species by (a) taxonomic group and (b) extinction risk category.

### Figure 5 (a, b):

@@

AquaMaps distribution map extent remaining after applying a presence threshold.  (a) A 40% threshold applied to all species in the AquaMaps dataset shows a mean loss of XXX, with a wide distribution in which some species lose nearly all of their apparent range.  (b) Mean (median) remaining extent at increments of presence threshold. Dark grey ribbon includes 25% to 75% quantiles, while light grey ribbon includes 9% to 91% quantiles.

### Figure 6
